\begin{rubric}{Employment History}
  \entry*[August 2024 -- Present]%
    \textbf{Graduate Research Assistant,} Nuclear, Plasma \& Radiological Engineering, University of Illinois Urbana-Champaign.
    \par - Developing adaptive mesh refinement methods and functional expansion tallies for unstructured mesh Monte Carlo particle transport.
    \par - Developing neutronics capabilities in Cardinal to enhance advanced reactor analysis methods and workflows.
  %
  \entry*[May 2026 -- August 2026]%
    \textbf{Research Aide Technical - PhD,} Computational Science, Argonne National Laboratory.
    \par - Implementing hybrid Woodcock delta tracking in the OpenMC Monte Carlo neutron transport code.
  %
  \entry*[May 2025 -- August 2025]%
    \textbf{Research Aide Technical - PhD,} Advanced Fuels and Materials, Argonne National Laboratory.
    \par - Investigated the effects of TRISO particle homogenization on heat transport in TRISO fueled microreactors.
    \par - Developed multi-scale methods to improve predictions of TRISO kernel temperatures during microreactor transients.
  %
  \entry*[May 2024 -- July 2024]%
    \textbf{Research Assistant,} Engineering Physics, McMaster University.
    \par - Developed methodologies to analyze surrogate TRISO fuel particles with HR(S)TEM and FIB-SEM instruments at the Canadian Center for Electron Microscopy.
    \par - Co-authored a journal manuscript on high-resolution microscopy methods for TRISO fuel.
  %
  \entry*[May 2022 -- April 2024]%
    \textbf{Graduate Research Assistant,} Department of Energy and Nuclear Engineering, Ontario Tech University.
    \par - Developed a discrete ordinates radiation transport solver and finite volume fluid activation/depletion solver in the MOOSE framework.
    \par - Coupled both solvers together for the purposes of analyzing fluid depletion in the health physics and environmental impact code CARIBOU.
    \par - Managed high performance computing resources within the Atkinson lab.
  %
  \entry*[September 2022 -- December 2023]%
    \textbf{Teaching Assistant,} Department of Energy and Nuclear Engineering, Ontario Tech University.
    \par Courses taught: \emph{Nuclear Plant Operations, Nuclear Reactor Kinetics, Medical Imaging}
  %
  \entry*[May 2021 -- August 2021]%
    \textbf{Undergraduate Research Assistant,} Department of Energy and Nuclear Engineering, Ontario Tech University.
    \par Project title: \emph{Literature Review of Small Modular Reactor Instrumentation and Control Strategies}.
    \par - Performed a literature review on Small Modular Reactor instrumentation and control strategies with a focus on integral Pressurized Water Reactors and High Temperature Gas-Cooled Reactors.
    \par - Assisted in preparing a manuscript for journal submission on the results of the literature review.
  %
  \entry*[May 2020 -- August 2020]%
    \textbf{Undergraduate Research Assistant,} Department of Energy and Nuclear Engineering, Ontario Tech University.
    \par Project title: \emph{Development of a Radioisotope Atmospheric Dispersion Model in the MOOSE Finite Element Framework}.
    \par - Performed a literature review on methods used for modeling radionuclide dispersion.
    \par - Developed a MOOSE mini-application to perform atmospheric dispersion calculations, simulating the first 24 hours of the Chernobyl plume.
  %
  \end{rubric}
